### 2018-06-22 Thesis/Parts/Discussion/Discussion.tex
Discussion p2

\subheader{Result analysis}
\subsubheader{Best performers}
The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on title. For the embeddings the TF-IDF weighted embedding works better than the others, although it is has is not a significant improvement compared to the default embeddings, which 1 median rank higher on abstract, and equal on title.

@@

\subsubheader{Journal plots}
Figure~\ref{figure:journalPlotNormal} show the journals in the, what we will refer to as "subject spectrum". We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject. In this figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left. We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
Figure~\ref{figure:journalPlotGroups} shows the journals, grouped with k-means on the original 300-dimensional embedding vector. On the bottom right hand side, the journals closest to the center point of the k-means algorithm are displayed. While most journal titles clearly state the research field, some do not. SAGE opens research area is social and behavioural sciences and humanities, RSC Advances' research area is chemical sciences and Orvosi hetilaps research area is experimental and clinical medicine. In the plot we can see that the original embedding-clustering is relatively well preserved, most groups stay clustered together. The central journals belong to mainly mixed groups, which is likely caused by either their general nature, or due to a collection of articles on the opposing ends of the spectrum.\\
The interactive version shows that the clusterings, as seen on both figure~\ref{figure:journalPlotNormal} \&~\ref{figure:journalPlotGroups} are subject based. Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions. It furthermore shows that the k-means groupings create an insight in research fields, although it is limited by the amount of groups the k-means algorithm creates. We found that our findings on the 2-dimensional representation of embeddings are simmilar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles.

\subheader{Improvements}
This research shows that, even tough the embeddings are able to capture and preserve relatedness, TF-IDF is able outperform the embeddings. Earlier research already proposed improvements to the word embeddings.
\citet{dai2015document} show that the usage of paragraph vectors improve the accuracy of word embeddings with 4.4\% on triplet creation with the wikipedia corpus, and a 3.9\% improvement on the same task based on the arXiv articles. Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative. While this looks promising, we have to keep in min that our task differs from earlier tasks, since we do not categorize on 2 categories, but on more than 3k. Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale.

>>>>

\subheader{Result analysis}
\begin{jumpin}
\subsubheader{Best performers}
The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on title. For the embeddings the TF-IDF weighted embedding works better than the others, although it is has is not a significant improvement compared to the default embeddings, which 1 median rank higher on abstract, and equal on title.

@@

\subsubheader{Journal plots}
Figure~\ref{figure:journalPlotNormal} show the journals in the, what we will refer to as "subject spectrum". We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject. In this figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left. We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
Figure~\ref{figure:journalPlotGroups} shows the journals, grouped with k-means on the original 300-dimensional embedding vector. On the bottom right hand side, the journals closest to the center point of the k-means algorithm are displayed. While most journal titles clearly state the research field, some do not. SAGE opens research area is social and behavioural sciences and humanities, RSC Advances' research area is chemical sciences and Orvosi hetilaps research area is experimental and clinical medicine. In the plot we can see that the original embedding-clustering is relatively well preserved, most groups stay clustered together. The central journals belong to mainly mixed groups, which is likely caused by either their general nature, or due to a collection of articles on the opposing ends of the spectrum.\\
The interactive version shows that the clusterings, as seen on both figure~\ref{figure:journalPlotNormal} \&~\ref{figure:journalPlotGroups} are subject based. Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions. It furthermore shows that the k-means groupings create an insight in research fields, although it is limited by the amount of groups the k-means algorithm creates. We found that our findings on the 2-dimensional representation of embeddings are simmilar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles.
\end{jumpin}
\subheader{Improvements}
This research shows that, even tough the embeddings are able to capture and preserve relatedness, TF-IDF is able outperform the embeddings. Earlier research already proposed improvements to the word embeddings.
\citet{dai2015document} show that the usage of paragraph vectors improve the accuracy of word embeddings with 4.4\% on triplet creation with the wikipedia corpus, and a 3.9\% improvement on the same task based on the arXiv articles. Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative. While this looks promising, we have to keep in min that our task differs from earlier tasks, since we do not categorize on 2 categories, but on more than 3k. Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale. \citet{pennington2014glove} showed that the GloVe model  outperforms the CBOW model, used in this research on a word analogy task. While using other methods may look promising, \citet{levy2015improving} observed that there were no major differences between the various method. They state that the difference in performance is manly caused by the global/hyper parameters. In this research,  we have not looked at comparison between various models and/or (hyper) parameters. We instead used a standard configuration, to focus more on the actual performance of the embeddings, instead of the best-possible performance.
